\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-20 paper.qmd
Add initial wordings for triangulation
Added initial setup for algorithm writing

@@

@@

>>>>

#### Computing hexagonal grid configurations

To define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($h_b$), width ($w_b$), need to compute the how many hexagons should represented by each axes in \kD{} space.

When $k=2$, the number of bins along the $x$ and $y$ axes, $b_1$ and $b_2$ should computed by accounting ${r_1, r_2}$, offset along the axes, and height ($h_b$), width ($w_b$).

@@

When $k = 2$

Delaunay triangulation of $C^{(k)}$ is a triangulation of the convex hull of $C^{(k)}$ such that the circumcircle of every triangle in the triangulation contains no other points from $C^{(k)}$.

@@

When $k=2$. which bin centroids should connected are identified as a result of triangulation. Therefore, corresponding \pD{} points should connected in the same order.

### 2024-04-20 paper.tex
Add initial wordings for triangulation
Added initial setup for algorithm writing

@@

@@

>>>>

\subsubsection{Computing hexagonal grid
configurations}\label{computing-hexagonal-grid-configurations}

To define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(h_b\)), width (\(w_b\)), need to compute the how many
hexagons should represented by each axes in \kD{} space.

When \(k=2\), the number of bins along the \(x\) and \(y\) axes, \(b_1\)
and \(b_2\) should computed by accounting \({r_1, r_2}\), offset along
the axes, and height (\(h_b\)), width (\(w_b\)).

@@

When \(k = 2\)

Delaunay triangulation of \(C^{(k)}\) is a triangulation of the convex
hull of \(C^{(k)}\) such that the circumcircle of every triangle in the
triangulation contains no other points from \(C^{(k)}\).

@@

When \(k=2\). which bin centroids should connected are identified as a
result of triangulation. Therefore, corresponding \pD{} points should
connected in the same order.
